\vspace{-2em}The 4th Workshop on Sustainable Software: Best Practices and Experiences (WSSSPE4)

### 2016-06-10 WSSSPE4_proposal/WSSSPE4_proposal.tex
some text fixes throughout, and BI addition

\title{The 4th Workshop on Sustainable Software: Best Practices and Experiences (WSSSPE4)
}
\author{Daniel S.\ Katz, University of Illinois Urbana--Champaign \\
        Gabrielle Allen, University of Illinois Urbana--Champaign \\
	Kyle E.\ Niemeyer, Oregon State University
	}
\date{}                                           % Activate to display a given date or no date

@@

{\bf \noindent Summary:} The WSSSPE4 workshop is part of a community driven effort to address the many new challenges that are evident for the development, deployment, maintenance, and sustainability of reusable software for academic research and education. These challenges include the software development process, the support and maintenance of software, governance and business models particularly for sustainability, the role of software in building science communities, the need for software to lead to science which is verifiable and reproducible, policy issues such as how to measure software impact, choose licensing, or assign software credit, and the education and nurturing of early stage researchers in scientific software. 
Based on successful WSSSPE1-WSSSPE3 meetings at SC13, SC14, and NCAR in 2013, 2014, and 2015, the organizers expect over 60 submitted papers and around 75 attendees at the WSSSPE4 meeting that will be held immediately preceding the RSE (Research Software Engineer) Conference in Manchester, UK, in September 2016.  As with previous events, WSSSPE4 will provide an open and dynamic forum for the community to discuss experiences and approaches in the areas listed above. This proposal requests funds to support attendance at WSSSPE4 for US based researchers, particularly targeted at encouraging attendance by early stage researchers with attention to diversity.

{\bf \noindent Intellectual Merit:} The participants will be selected using a formal application procedure, with selection criteria based around (1) the potential of their attendance to contribute towards their own research and educational goals; (2) their potential contribution to the workshop; (3) providing a diverse set of attendees with priority to early stage researchers (e.g. students, postdoctoral researchers, early stage faculty). The workshop will include vision and position papers as well as lightning talks and demos, aimed at improving sustainable scientific software today as well as defining and working towards the its future.

{\bf \noindent Broader Impacts:} WSSSPE4 accepted submissions (except presentations of previously published work) are planned to be published by WSSSPE as a special collection in http://ceur-ws.org/, which is fully indexed.
Other material from the workshop will be openly archived on public popular sites (e.g. Figshare, Slideshare, arXiv). It is anticipated that the workshop will again be tweeted and documented live including contributions from external participants. The organizers take seriously the responsibility to encourage participation from underrepresented groups as workshop leaders as well as attendees, and NSF funds will be used to encourage such participation from the US community.

@@

This is the fourth major event in the WSSSPE series. The first two WSSSPE workshops were held as part of SC in 2013 and 2014. These one-day workshops brought together researchers and practitioners to discuss challenges and issues around the development, deployment and maintenance of reusable software for academic research and education, and discussed potential solutions, moving from a presentation to a presentation and discussion format.  Reports from these workshops, and set of extended papers from them, have been published in special collections of the Journal of Open Research Software \cite{WSSSPE1-collection, WSSSPE2-collection, WSSSPE1, WSSSPE2}.
WSSSPE3, held at NCAR in 2015, grew out of the previous events, and focused almost entirely on facilitated discussions, with the aim of starting working groups to make changes in the practice of scientific software development leading to more sustainable software.  Two of these groups have continued
working together, leading to the FORCE11 Software Citation Principles and an in-progress paper
on best practices for sustainable scientific software development.  The report from WSSSPE3 has been submitted to the Journal of Open Research Software and is currently available as a preprint on arXiv~\cite{WSSSPE3}.

@@

The participants will be selected using a formal application procedure which will be described and advertised on the workshop web page, with selection criteria based around (1) the potential of their attendance to contribute towards their own research and educational goals; (2) their potential contribution to the workshop; (3) providing a diverse set of attendees with priority to early stage researchers (e.g. students, postdoctoral researchers, early stage faculty).

>>>>

\title{\vspace{-2em}The 4th Workshop on Sustainable Software: Best Practices and Experiences (WSSSPE4)
}
\author{Daniel S.\ Katz, University of Illinois Urbana--Champaign \\
        Gabrielle Allen, University of Illinois Urbana--Champaign \\
	Kyle E.\ Niemeyer, Oregon State University
	}
\date{}                                           % Activate to display a given date or no date

@@

\noindent \textbf{Summary:} The WSSSPE4 workshop is part of a community driven effort to address the many new challenges that are evident for the development, deployment, maintenance, and sustainability of reusable software for academic research and education. These challenges include the software development process, the support and maintenance of software, governance and business models particularly for sustainability, the role of software in building science communities, the need for software to lead to science which is verifiable and reproducible, policy issues such as how to measure software impact, choose licensing, or assign software credit, and the education and nurturing of early stage researchers in scientific software. 
Based on successful WSSSPE1--WSSSPE3 meetings at SC13, SC14, and NCAR in 2013, 2014, and 2015, the organizers expect over 60 submitted papers and around 75 attendees at the WSSSPE4 meeting that will be held immediately preceding the RSE (Research Software Engineer) Conference in Manchester, UK, in September 2016.  As with previous events, WSSSPE4 will provide an open and dynamic forum for the community to discuss experiences and approaches in the areas listed above. This proposal requests funds to support attendance at WSSSPE4 for US based researchers, particularly targeted at encouraging attendance by early stage researchers with attention to diversity.

\noindent \textbf{Intellectual Merit:} The participants will be selected using a formal application procedure, with selection criteria based around (1) the potential of their attendance to contribute towards their own research and educational goals; (2) their potential contribution to the workshop; (3) providing a diverse set of attendees with priority to early stage researchers (e.g., students, postdoctoral researchers, early stage faculty). The workshop will include vision and position papers as well as lightning talks and demos, aimed at improving sustainable scientific software today as well as defining and working towards the its future.

\noindent \textbf{Broader Impacts:} WSSSPE4 accepted submissions (except presentations of previously published work) are planned to be published by WSSSPE as a special collection in \url{http://ceur-ws.org/}, which is fully indexed.
Other material from the workshop will be openly archived on public popular sites (e.g., Figshare, Slideshare, arXiv). It is anticipated that the workshop will again be tweeted and documented live including contributions from external participants. The organizers take seriously the responsibility to encourage participation from underrepresented groups as workshop leaders as well as attendees, and NSF funds will be used to encourage such participation from the US community. 
Strategies for reaching\slash recruiting such participants will be solicited from members of the Program Committee with experience supporting students, researchers, and research software engineers with such backgrounds.

@@

This is the fourth major event in the WSSSPE series. The first two WSSSPE workshops were held as part of SC in 2013 and 2014. These one-day workshops brought together researchers and practitioners to discuss challenges and issues around the development, deployment and maintenance of reusable software for academic research and education, and discussed potential solutions, moving from a presentation to a presentation and discussion format.  Reports from these workshops, and set of extended papers from them, have been published in special collections of the \textit{Journal of Open Research Software} \cite{WSSSPE1-collection, WSSSPE2-collection, WSSSPE1, WSSSPE2}.
WSSSPE3, held at NCAR in 2015, grew out of the previous events, and focused almost entirely on facilitated discussions, with the aim of starting working groups to make changes in the practice of scientific software development leading to more sustainable software. Two of these groups have continued
working together, leading to the FORCE11 Software Citation Principles and an in-progress paper
on best practices for sustainable scientific software development.  The report from WSSSPE3 has been submitted to the \textit{Journal of Open Research Software} and is currently available as a preprint on arXiv~\cite{WSSSPE3}.

@@

The participants will be selected using a formal application procedure which will be described and advertised on the workshop web page, with selection criteria based around (1) the potential of their attendance to contribute towards their own research and educational goals; (2) their potential contribution to the workshop; (3) providing a diverse set of attendees with priority to early stage researchers (e.g., students, postdoctoral researchers, early stage faculty).
